---
title: "module1.1"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Importing tidyverse
```{r}
library(tidyverse)
```

##Importing data
```{r}
df <- read.csv("~/Desktop/Soybeanandlightdata.csv")
glimpse(df)
```

## Grouping 
Group so that you can see the mean and standard deviation of height by genotype
```{r}
df$Height <- as.numeric(df$Height)
df2<-df%>%
  group_by(Genotype) %>%
  summarise(mean.Height = mean(Height, na.rm = TRUE),
            sd.Height = sd(Height, na.rm = TRUE))
glimpse(df2)
```

##Split-Apply-Combine
We want to see how genotype and treatment combined yield height
```{r}
df3 <-df %>% 
  group_by(Genotype, Treatment) %>%
  summarise(mean.Height = mean(Height, na.rm = TRUE),
            sd.Height = sd(Height, na.rm = TRUE), .groups = "drop")
head(df3)
```

## Plot
Use a bar graph to visualize the height differences comparing the genotype's different treatments
```{r pressure, echo=FALSE}
p <- ggplot(data=df3, aes(x=Genotype, y=mean.Height, fill=Treatment)) +
  geom_bar(stat="identity", position="dodge") +
  theme_bw(base_size = 6)
p
```
## Analysis
In most Genotypes, you can tell from the graph that the Red-Blue light treatment significantly decreased the height of the plant in almost all genotypes.

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
